\documentclass[letterpaper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{tabularx}
% Set spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

% \titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

%===== Header =====
{\LARGE \textbf{Thilina H. Weerakkody}}
% \\
% \textit{Data Analytics | Robotics | Research Automation}\\
% \vspace{0.5em}

\faIcon{map-marker-alt} Los Angeles, CA \quad
\faIcon{envelope} \href{mailto:thilinahweerakkody@gmail.com}{thilinahweerakkody@gmail.com} \quad
% \faIcon{globe} \href{https://sites.google.com/view/thilinahw}{sites.google.com/view/thilinahw} \\
\faIcon{linkedin} \href{https://www.linkedin.com/in/thilinahw/}{linkedin.com/in/thilinahw} \quad
\faIcon{github} \href{https://github.com/thilinahwe}{github.com/thilinahwe}

%===== Summary =====
\section*{Professional Summary \hrulefill}
Versatile data analyst and engineer with a Ph.D. in Mechanical Engineering and deep experience in robotics, control systems, and data acquisition. Strong background in sensor integration, signal processing, and data-driven modeling. Passionate about solving complex problems with data, developing robust automation workflows, and creating actionable insights from real-world experiments.

%===== Skills =====
\section*{Technical Skills \hrulefill}

\begin{tabularx}{\textwidth}{p{1.2in} p{4.4in}}
\textbf{Languages:} & Python, MATLAB, C/C++, SQL, Julia \\
\textbf{Data Tools:} & Pandas, NumPy, Matplotlib, scikit-learn, TensorFlow (basic) \\
\textbf{Visualization:} & Tableau, Seaborn, Excel \\
\textbf{Tools:} & Git, Jupyter, LabVIEW, ROS, \LaTeX \\
\textbf{Hardware:} & Arduino, Raspberry Pi, Teensy, OpenBCI \\
\textbf{CAD/Simulation:} & SolidWorks, Fusion 360, COMSOL, MATLAB/Simulink \\
\end{tabularx}

%===== Projects =====
\section*{Selected Projects \hrulefill}
\textbf{High-Throughput Radiochemistry Imaging System – UCLA}  
Developed LabVIEW-controlled robotic imaging platform with automated image acquisition, bin file storage, and metadata logging. Parsed XML configurations to optimize imaging workflows and integrate sensor-based decision logic.

\textbf{Adaptive Control for SMA-based Systems – University of Iowa}  
Modeled nonlinear, hysteretic behaviors in shape memory actuators. Applied $\mathcal{L}_1$ adaptive control strategies and visualized system response using MATLAB. Analyzed time-series datasets for actuator performance under varying conditions.

% \textbf{GitHub Data Analytics Portfolio (In Progress)}  
% Building a set of public analytics projects including time-series signal clustering, imaging data exploration, and EDA using Pandas and Seaborn.  
% \href{https://github.com/thilinahwe}{\faIcon{github} github.com/thilinahwe}

%===== Work Experience =====
\section*{Professional Experience \hrulefill}
\textbf{Postdoctoral Research Scholar – UCLA} \hfill 2024–Present \\
Led automation of high-throughput radiochemistry systems. Created scalable data pipelines for experimental imaging workflows using Python, LabVIEW, and embedded control. Developed documentation for reproducibility.

\textbf{Graduate Research Assistant – University of Iowa} \hfill 2019–2024 \\
Developed adaptive control and data acquisition systems for soft robotics. Designed control logic, conducted experimental validation, and processed actuator data. Employed signal filtering, regression modeling, and multibody simulation.

%===== Education =====
\section*{Education \hrulefill}
\textbf{Ph.D. in Mechanical Engineering}, University of Iowa, IA \hfill 2019--2024\\
Dissertation: Design and Control of Artificial Muscles for Robotic Applications%\\
% \textit{Advisors: Dr. Caterina Lamuta, Dr. Venanzio Cichella}

\textbf{B.Sc. (Hons.) in Mechanical Engineering}, University of Moratuwa, Sri Lanka \hfill 2011--2016

\textbf{Diploma in Information Technology}, British Computer Society (UK) \hfill 2012--2014 
%===== Certifications =====
\section*{Certifications \hrulefill}
\begin{itemize}[leftmargin=1em]
  \item Google Data Analytics Professional Certificate – Coursera
  % \item Diploma in Information Technology – British Computer Society (2012–2014)
\end{itemize}

%===== Publications (Optional) =====
% You can comment this section out or trim it
\section*{Publications (Selected) \hrulefill}
\begin{itemize}[leftmargin=1em]
    \item Weerakkody, T.H. et al., "Modeling and control of twisted and coiled artificial muscles", \textit{Meccanica}, 2023.
    \item Weerakkody, T.H. et al., “Robust and adaptive sampled-data control...”, \textit{IEEE Control Systems Letters}, 2021.
\end{itemize}

%===== Personal Details =====
\section*{Additional Information \hrulefill}
\textbf{Citizenship:} Sri Lankan \\
\textbf{Visa:} F-1 OPT (STEM Eligible) \\
\textbf{Languages:} English (Fluent), Sinhala (Native) \\

\vspace{0.5em}
\textit{Last Updated – \today}

\end{document}
